Age-related changes in plant growth and traits

### 2016-05-26 nutrient.Rmd
nutrient data plots

plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)

@@

pdf("figs2/Nutrients/age_by_species_NP.pdf", height=7.5, width=11)
plot
for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
data <- subset(nutrient,species==i)
plot(P~N,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(1,200,i)
data2 <- subset(data,tissue_simple=="reproductive")
text(P~N,data2,label=data2$tissue_complete,col="red")
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
}
dev.off()

>>>>

pdf("figs2/Nutrients/soil.pdf", height=6, width=6)
plot
plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
dev.off()

@@

pdf("figs2/Nutrients/age_by_species_NP.pdf", height=7.5, width=11)
plot
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05)) 
for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
data <- subset(nutrient,species==i)
plot(P~N,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(1,200,i)
data2 <- subset(data,tissue_simple=="reproductive")
text(P~N,data2,label=data2$tissue_complete,col="red",cex=0.7)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")

plot(P~K,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(.4,200,i)
data2 <- subset(data,tissue_simple=="reproductive")
text(P~K,data2,label=data2$tissue_complete,col="red",cex=0.7)
#legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
#legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
}
dev.off()
